\section{\texttt{history} - Operations History}

\begin{tabular}{r|l}
    Maintainer & John Vidler (\href{mailto:j.vidler@lancaster.ac.uk}{j.vidler@lancaster.ac.uk}) \\
    Version & 1.0.0 \\
    Last Updated & 12 June 2017 \\
\end{tabular} \vspace{1em}

A top-level namespace conforming to the \texttt{history} namespace specification that describes the processing history of this file. Complies with the interface specification and thus has an inner \texttt{\_\_version\_\_} field.

The complete structure for the \texttt{history} namespace is as follows (newlines inserted for clarity, and values skipped for brevity):

\begin{lstlisting}
{
    "__version__": "1.0.0",
    "log": [
        { "binary": "...", "time": "...", "args": "...", "platform": "...", "md5": "..." },
        { "binary": "...", "time": "...", "args": "...", "platform": "...", "md5": "..." }
    ]
}
\end{lstlisting}

Note that the $log$ field is an array of operations, which may contain any number of entries, including zero.


\subsection{\texttt{\_\_version\_\_}}
(String, Required)

The SemVer (see \ref{sec:SemanticVersioning}) compliant version that this history meta-block complies with, currently at 1.0.0.


\subsection{\texttt{log}}
(Array, Optional)

The array of logged actions, each entry should be a log-object.
If this field is absent, compliant parser implementations should interpret this as a zero-length array (no logged actions).
Each object in this array should have at least a $binary$ and $time$ field, but may also optionally include $args$, $platform$, and $md5$ fields as required.

\textbf{NOTE:} The log entries are likely to be an in-time-order array, but if you require guaranteed true time-order listing, ensure the parsing application sorts by the $time$ field.

\subsubsection{\texttt{binary}}
(String, Required)

The binary executed on this file.
If possible, non-system specific paths should be used to aid with compatibility between platforms.

\subsubsection{\texttt{time}}
(String, Required)

An ISO8601\cite{ISO/8601} format string for when the binary was executed.

\subsubsection{\texttt{args}}
(String, Optional)

Any command-line arguments that were passed to the binary for this log entry.
Quotes must be escaped in the string to comply with the JSON specification.

\subsubsection{\texttt{platform}}
(String, Optional)

The dot-delimited platform and architecture that this command was executed on.
Examples of possible values are shown below, but any valid $platform.arch$ string is permissible.

\begin{itemize}
    \item{Linux.x86}
    \item{Linux.x64}
    \item{Linux.ARMv7LE}
    \item{Linux.ARMv7BE}
    \item{Windows.x86}
    \item{Windows.x64}
    \item{osX.x86}
    \item{osX.x64}
\end{itemize}


\subsubsection{\texttt{md5}}
(String, Optional)

The MD5 hash string of the binary executed for this log entry.


\section{Example}

\lstinputlisting{examples/ns-history/example-json.json}

\noindent\textit{(NOTE: Linebreaks, indentation, and spacing added for readability but not required for the header to function)}